---
title: "DDP Course Project"
author: "WYL"
date: "October 19, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny application overview

This app is related to the course project at data-products in coursera!   

This app is a linear regression of the outcome mpg for each variable in the mpg dataset.

The result including two part:  
1. summary linear regrssion model.  
2. show scatter plot and add fit line on it

## How to use this App

1. open the following link: https://wangyl2665.shinyapps.io/shinyappddp/
2. select one predictor from drop-down memu.
3. you will see the summary about line regression model and scatter plot 

## Plot Output in R

```{r, echo = TRUE}
fit <- lm(mpg ~ disp, data = mtcars)
plot(mpg ~ disp, data = mtcars, pch = 19, col = 'red')
abline(fit, col = 'blue', lwd = 4)
```

## Links

Shiny App URL: https://wangyl2665.shinyapps.io/shinyappddp/
Github Repository URL: https://github.com/wangyl2665/DDP

